### 2018-05-28 write-up/abstract.tex
Separate out acknowledgements onto its own sheet

\newpage
{\normalfont\Huge\sffamily\bfseries Abstract}
\vspace{24pt}

@@

\vspace*{\fill}
{\normalfont\Huge\sffamily\bfseries Acknowledgements}

I would like to thank my family and closest friends for supporting me through
my time at Cambridge: you have been my strength when I have had none. I would
also like to thank my supervisors, Dr\@.~Neelankantan Krishnaswami and
Dr\@.~Stephen Dolan, for teaching me so much this year. I owe a debt of
gratitude to both the 2017 Part III Appeals Committee and those who wrote
letters in support of my appeal, for believing I deserved the chance to stay
on: never have I valued the privilege of learning what I enjoy and enjoying
what I learn more.  Lastly, I would like to thank the many staff and research
members of the Computer Lab who have been approachable, patient and attentive
during my time here.

\newpage
\vspace*{\fill}

>>>>

% {\normalfont\Huge\sffamily\bfseries Abstract}
% \vspace{24pt}
\begin{abstract}

@@

\end{abstract}

\vspace*{\fill}
\cleardoublepage%

{\normalfont\Huge\sffamily\bfseries Acknowledgements}
\vspace{24pt}

I would like to thank my family and closest friends for supporting me through
my time at Cambridge: you were my strength when I had none. I would also like
to thank my supervisors, Dr\@.~Neelakantan Krishnaswami and Dr\@.~Stephen
Dolan, for teaching me so much this year. I owe a debt of gratitude to both the
2017 Part III Appeals Committee and those who wrote letters in support of my
appeal, for believing I deserved the chance to stay on: never have I valued the
privilege of learning what I enjoy and enjoying what I learn more.  Lastly, I
would like to thank the many staff and research members of the Computer Lab who
have been approachable, patient and attentive during my time here.

\vspace*{\fill}
\cleardoublepage%
